DataGatheringandAnalysis

### 2014-11-13 GEMDataSource.Rmd
Accept edit
Merge of Perceived Capabilities into FinalGEM

# Change years from columns to rows and create CPreceivedCapabilities
CPerceivedOpportunities<- melt(data = PerceivedOpportunities,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

@@

FinalMerge <- merge(MergedGem2, MergedGem3,
                   union("Country", "Year"),
                   all = TRUE)

# Convert percent columns from character to numeric
FinalMerge[,"PercentPerceived"] <- as.numeric(FinalMerge[,"PercentPerceived"])
FinalMerge[,"PercentFear"] <- as.numeric(FinalMerge[,"PercentFear"])
FinalMerge[,"PercentNascent"] <- as.numeric(FinalMerge[,"PercentNascent"])
FinalMerge[,"PercentOwner"] <- as.numeric(FinalMerge[,"PercentOwner"])
FinalMerge[,"PercentIntention"] <- as.numeric(FinalMerge[,"PercentIntention"])

# Check data to confirm change
summary(FinalMerge)

# Run a linear regression
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear, data = FinalMerge)
summary(R1)

@@

# Run a linear regression
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalMerge)
summary(R2)

@@

# Run a linear regression
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalMerge)
summary(R3)

@@

# Plot graph
car::scatterplotMatrix(FinalMerge)

@@

# Merge GDPGrowth and FinalMerge
CompeteDataset <- merge(FinalMerge, GDPGrowth,
                   union("Country", "Year"),
                   all = TRUE)

>>>>

# Change years from columns to rows and create CPreceivedOpportunities
CPerceivedOpportunities<- melt(data = PerceivedOpportunities,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

@@

MergedGem4 <- merge(MergedGem2, MergedGem3,
                   union("Country", "Year"),
                   all = TRUE)

FinalGEM <- merge(MergedGem4, CPerceivedOpportunities,
                   union("Country", "Year"),
                   all = TRUE)

# Convert percent columns from character to numeric
FinalGEM[,"PercentPerceived"] <- as.numeric(FinalGEM[,"PercentPerceived"])
FinalGEM[,"PercentFear"] <- as.numeric(FinalGEM[,"PercentFear"])
FinalGEM[,"PercentNascent"] <- as.numeric(FinalGEM[,"PercentNascent"])
FinalGEM[,"PercentOwner"] <- as.numeric(FinalGEM[,"PercentOwner"])
FinalGEM[,"PercentIntention"] <- as.numeric(FinalGEM[,"PercentIntention"])
FinalGEM[,"PercentOpportunities"] <- as.numeric(FinalGEM[,"PercentOpportunities"])

# Check data to confirm change
summary(FinalGEM)

# Run a linear regression
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear, data = FinalGEM)
summary(R1)

@@

# Run a linear regression
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalGEM)
summary(R2)

@@

# Run a linear regression
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalGEM)
summary(R3)

@@

# Plot graph
car::scatterplotMatrix(FinalGEM)

@@

# Merge GDPGrowth and FinalMerge
CompeteDataset <- merge(FinalGEM, GDPGrowth,
                   union("Country", "Year"),
                   all = TRUE)
